### 2022-07-26 sections/background_estimation.tex

In the hadronic channels, the contribution of fakes is estimated from data using the fake-factor (FF) method to derive the transfer functions from the background-enriched control
regions (CR) to the SR~\cite{HIGG-2018-14}.
%by defining control regions (CR)
%enriched in misidentified
%tau candidates via loosened tau requirements with fake factors and partially from MC~\cite{ATLAS-CONF-2021-044}.
These CRs do not overlap with the main signal regions discussed in Section~\ref{sec:strategy_Htautau}.
The CR selection requirements are analogous to those used to define signal regions, except
that the subleading $\tau$ candidate is required to fail the `medium' $\tau$ identification while still passing a loose requirement.
The contribution of fakes with subleading $\tau$ candidates can be calculated by rescaling the templates for `loose' $\tau$ candidates in the CR
with the FFs.
The templates are produced by subtracting all MC background contributions with real subleading $\tau$-leptons from the data.
The FFs are computed as the ratio of misidentified $\thad$ candidates that either pass or fail the `medium' $\tau$ ID selection in regions enriched in events originating from 
$W$+jets processes~\cite{HIGG-2018-14}. 
%the Data-MC ($\mathrm{real~tau}$) ratio of the yields of events in which the tau candidate is passing or failing the medium tau ID selection
%in the $W$+jets samples~\cite{ATLAS-CONF-2021-044}.
%passing to failing the medium tau ID in the $W$+jets control region.
%We have compared
FFs obtained from the $W$+jets events are compared with those from the same-sign $\thadhad$ control regions and the differences are treated as systematic uncertainties.

>>>>

In the hadronic channels, the contribution of fakes is estimated from data using the fake-factor (FF) method to derive the transfer functions from the background-enriched control
regions (CR) to the SR~\cite{HIGG-2019-09}.
%by defining control regions (CR)
%enriched in misidentified
%tau candidates via loosened tau requirements with fake factors and partially from MC~\cite{ATLAS-CONF-2021-044}.
These CRs do not overlap with the main signal regions discussed in Section~\ref{sec:strategy_Htautau}.
The CR selection requirements are analogous to those used to define signal regions, except
that the subleading $\tau$ candidate is required to fail the `medium' $\tau$ identification while still passing a loose requirement.
The contribution of fakes with subleading $\tau$ candidates can be calculated by rescaling the templates for `loose' $\tau$ candidates in the CR
with the FFs.
The templates are produced by subtracting all MC background contributions with real subleading $\tau$-leptons from the data.
The FFs are computed as the ratio of misidentified $\thad$ candidates that either pass or fail the `medium' $\tau$ ID selection in regions enriched in events originating from 
$W$+jets processes~\cite{HIGG-2019-09}. 
%the Data-MC ($\mathrm{real~tau}$) ratio of the yields of events in which the tau candidate is passing or failing the medium tau ID selection
%in the $W$+jets samples~\cite{ATLAS-CONF-2021-044}.
%passing to failing the medium tau ID in the $W$+jets control region.
%We have compared
FFs obtained from the $W$+jets events are compared with those from the same-sign $\thadhad$ control regions and the differences are treated as systematic uncertainties.

### 2022-07-26 sections/statistical_analysis.tex

The test statistic $q_\mu$ is defined as the profile likelihood ratio, 
$q_\mu = -2\ln({\cal L}(\mu,{\hat{\hat{\theta}}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and the ${\hat{\hat{\theta}}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
%A related statistic is used to determine whether the observed data is compatible with the background-only hypothesis (the so-called discovery test)  
%by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
%The $p$-value (referred to as $p_0$), representing the level of agreement between the data and the background-only hypothesis, is estimated by integrating
%%representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
%%the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
%the distribution of $q_0$ based on the asymptotic formulae in Ref.~\cite{Cowan:2010js}, 
%above the observed value of $q_0$ in the data. 
%%The observed $p_0$-value is checked for each explored signal scenario.
%%In the case of the data being compatible with the background-only hypothesis, 
%Upper limits on $\mu$, and thus on 
%$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
%For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
%where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

>>>>

The test statistic $q_\mu$ is defined as the profile likelihood ratio, 
$q_\mu = -2\ln({\cal L}(\mu,{\hat{\hat{\theta}}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $\hat{\mu} \geq 0$), and the ${\hat{\hat{\theta}}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
%A related statistic is used to determine whether the observed data is compatible with the background-only hypothesis (the so-called discovery test)  
%by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
%The $p$-value (referred to as $p_0$), representing the level of agreement between the data and the background-only hypothesis, is estimated by integrating
%%representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
%%the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
%the distribution of $q_0$ based on the asymptotic formulae in Ref.~\cite{Cowan:2010js}, 
%above the observed value of $q_0$ in the data. 
%%The observed $p_0$-value is checked for each explored signal scenario.
%%In the case of the data being compatible with the background-only hypothesis, 
%Upper limits on $\mu$, and thus on 
%$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
%For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
%where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.
